plantecophys - an R package for analysing and modelling leaf gas exchange data

### 2015-10-12 manuscript.Rmd
More logical organization
README update and minor edits

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Load packages and custom functions
source("R/load.R")

@@

\
Finally we can combine the biochemical demand function of photosynthesis (Eq. 1) with the supply function (Eq. 2) and an expression for the dependency of g~s~ on environmental drivers (Eq. 3). This 'coupled' leaf gas exchange model [@leuning1990; @collatz1991; @leuning1995] is implemented in many process-based ecosystem and global land surface models [@wang1998; @bonan2014; @duursma2012; @sellers1997]. This model allows prediction of A~n~, g~s~ and leaf transpiration rate in response to all major environmental drivers (except soil water limitation), and key leaf traits (g~1~, V~cmax~, J~max~, R~d~, and their temperature dependencies).

@@

The main tools included in the plantecophys package are to a) fit A-C~i~ curves to estimate V~cmax~, J~max~ and R~d~, b) fit Ball-Berry type models, c) simulate from the coupled leaf gas exchange model and d) calculate the optimal stomatal conductance. A list of the key functions in the package are summarized in Table 1.

```{r results='asis', echo=FALSE, message=FALSE, warn=FALSE}
f <- c("`fitaci`","`fitBB`","`FARAO`","`Photosyn`","`PhotosynEB`","`AciC4`", "`RHtoVPD` etc.")
d <- c("Fit, summarize, plot and simulate photosynthesis-[CO~2~] response curves (A-Ci curves)",
"Fit Ball-Berry type models of stomatal conductance",
"Estimate optimal stomatal conductance with a numerical implementation of the Cowan-Farquhar hypothesis",
"Simulate C3 photosynthesis and transpiration with the coupled leaf gas exchange model. Also simulates the FvCB model when either C~i~ or g~s~ is given as input. For C4 photosynthesis, see `AciC4`",
"Estimate leaf temperature from energy balance, when a significant leaf boundary layer is present",
"Simulates the dependence of C4 photosynthesis on the intercellular CO~2~ concentration",
"Convert between commonly used units (relative humidity, vapour pressure deficit, dewpoint temperature)")
df <- data.frame(Function=f, Description=d)

@@

\
All code used in this article (including the code to generate the article written in markdown, all figures and full example code), can be downloaded from http://www.github.com/duursma2015plosone.

@@

\
**Figure 2**. Standard output from the `fitaci` function. A~n~ is the net photosynthetic rate, C~i~ the intercellular CO~2~ concentration. Symbols are measurements, the black line the fitted FvCB model of photosynthesis. Colored lines indicate the two photosynthesis rates in the FvCB model. In the default mode, the `fitaci` function estimates V~cmax~, J~max~ and R~d~ from the fitted curve. Optionally, R~d~ is provided as an input, for example when it was measured separately. In this example, V~cmax~ was estimated as `r round(fitc["Vcmax","Estimate"],1)` (SE `r round(fitc["Vcmax","Std. Error"],2)`), J~max~ was `r round(fitc["Jmax","Estimate"],1)` (SE `r round(fitc["Jmax","Std. Error"],2)`) and R~d~ was `r round(fitc["Rd","Estimate"],1)` (SE `r round(fitc["Rd","Std. Error"],2)`). Assumed parameters were K~m~ = `r round(exfit1$Km,0)` and $\Gamma}^{∗}$ = `r round(exfit1$GammaStar,1)` (all in units of $\mu$mol m^-2^ s^-1^). The R^2^ of a regression of measured vs. fitted was 0.99.

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Load packages and custom functions
source("load.R")

@@

\
Finally we can combine the biochemical demand function of photosynthesis (Eq. 1) with the supply function (Eq. 2) and an expression for the dependency of g~s~ on environmental drivers (Eq. 3). This 'coupled' leaf gas exchange model [@leuning1990; @collatz1991; @leuning1995] is implemented in many process-based ecosystem and global land surface models [@wang1998; @bonan2014; @duursma2012; @sellers1997]. This model allows prediction of A~n~, g~s~ and leaf transpiration rate in response to all major environmental drivers (except soil water limitation), and incorporates key leaf traits (g~1~, V~cmax~, J~max~, R~d~, and their temperature dependencies).

@@

The main tools included in the plantecophys package are to a) fit A-C~i~ curves to estimate V~cmax~, J~max~ and R~d~, b) fit Ball-Berry type models, c) simulate from the coupled leaf gas exchange model and d) calculate the optimal stomatal conductance. The key functions in the package are summarized in Table 1.

```{r results='asis', echo=FALSE, message=FALSE, warn=FALSE}
f <- c("`fitaci`","`fitBB`","`FARAO`","`Photosyn`","`PhotosynEB`","`AciC4`", "`RHtoVPD` etc.")
d <- c("Fit, summarize, plot and simulate photosynthesis-[CO~2~] response curves (A-Ci curves)",
"Fit Ball-Berry type models of stomatal conductance",
"Estimate optimal stomatal conductance with a numerical implementation of the Cowan-Farquhar hypothesis",
"Simulate C3 photosynthesis and transpiration with the coupled leaf gas exchange model. Also simulates the FvCB model when either C~i~ or g~s~ is given as input.",
"Estimate leaf temperature from energy balance, when a significant leaf boundary layer is present",
"Simulates the dependence of C4 photosynthesis on the intercellular CO~2~ concentration",
"Convert between commonly used units (relative humidity, vapour pressure deficit, dewpoint temperature)")
df <- data.frame(Function=f, Description=d)

@@

\
All code used in this article (including the code to generate the article written in markdown, all figures and full example code), can be downloaded from http://www.github.com/duursma2015plosone. The repository also includes code to demonstrates how to extract additional statistics from fitted A-C~i~ curves.

@@

\
**Figure 2**. Standard output from the `fitaci` function. A~n~ is the net photosynthetic rate, C~i~ the intercellular CO~2~ concentration. Symbols are measurements, the black line the fitted FvCB model of photosynthesis. Colored lines indicate the two photosynthesis rates in the FvCB model. In the default mode, the `fitaci` function estimates V~cmax~, J~max~ and R~d~ from the fitted curve. Optionally, R~d~ is provided as an input, for example when it was measured separately. In this example, V~cmax~ was estimated as `r round(fitc["Vcmax","Estimate"],1)` (SE `r round(fitc["Vcmax","Std. Error"],2)`), J~max~ was `r round(fitc["Jmax","Estimate"],1)` (SE `r round(fitc["Jmax","Std. Error"],2)`) and R~d~ was `r round(fitc["Rd","Estimate"],1)` (SE `r round(fitc["Rd","Std. Error"],2)`). Assumed parameters were K~m~ = `r round(exfit1$Km,0)` and ${\Gamma}^{∗}$ = `r round(exfit1$GammaStar,1)` (all in units of $\mu$mol m^-2^ s^-1^). The R^2^ of a regression of measured vs. fitted was 0.99.
